\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{ragged2e}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Roudy Hajo} \\ \vspace{1pt}
    \small +33 7 67 42 56 59 $|$ \href{mailto:roudy.hajo2003@gmail.com}{\underline{roudy.hajo2003@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/roudy-hajo/}{\underline{linkedin.com/in/roudy-hajo}} $|$
    \href{https://github.com/roudy-h}{\underline{github.com/roudy-h}}
\end{center}

% texte en justifié
\begin{justify}
    Final year Computer Science student at Polytech Nantes School of Engineering with a passion for software development, network and cloud computing. Experienced in developing full-stack web applications, REST APIs, and conducting research in Database Systems. Strong problem-solving skills and a proven track record of delivering high-quality projects.
\end{justify}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Polytech Nantes School of Engineering}{Nantes, France}
      {Master's Degree in Computer Science specialization in Network, Security, Cloud Computing}{Sep. 2024 -- Aug 2027}
    \resumeSubheading
      {University Institute of Technology of Nantes}{Nantes, France}
      {Technical Associate’s Degree in Computer Science}{Sep. 2022 -- Jun 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Research Intern in Database Systems}{May 2026 -- Aug 2026}
      {Coimbra Institute of Engineering}{Coimbra, Portugal}
      \resumeItemListStart
        \resumeItem{Designed a decentralized multi-agent architecture utilizing Quantum Neural Networks (QNN) and reinforcement learning to optimize database index tuning.}
        \resumeItem{Engineered an adaptive centralized learning router to eliminate workload skew and dynamically balance queries across replicas.}
      \resumeItemListEnd
        
    \resumeSubheading
      {Web Developer Intern}{May 2025 -- July 2025}
      {Nantes University -- Digital and Information Systems Department (DSIN)}{Nantes, France}
      \resumeItemListStart
        \resumeItem{Updated and adapted the Symfony web application 'Syllabus' to dynamically present the university's course offerings to students.}
      \resumeItemListEnd

    \resumeSubheading
      {Web Developer Intern}{Apr 2024 -- June 2024}
      {Kookline -- Web Development Agency}{Nantes, France}
      \resumeItemListStart
        \resumeItem{Developed a responsive website using the WordPress Content Management System (CMS) for skydiving reservations and online services.}
    \resumeItemListEnd

    \resumeSubheading
      {Academic Tutor}{Oct 2023 -- July 2024}
      {University Institute of Technology of Nantes}{Nantes, France}
      \resumeItemListStart
        \resumeItem{Mentored and guided first-year students in fundamental computer science courses, focusing on algorithms, core programming principles, and mathematics.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\href{https://github.com/roudy-h/todo-api}{TODO App}} $|$ \emph{Spring Boot, Java, Maven, Angular}}{Oct 2025 -- June 2026}
        \resumeItemListStart
          \resumeItem{Developed a responsive full-stack task management web application supporting secure CRUD operations.}
          \resumeItem{Implemented dynamic client-side routing with Angular and engineered reactive RESTful APIs with Spring Boot.}
        \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://oniris-polytech.univ-nantes.io/sketchoscent/}{SketchOscent}} $|$ \emph{HTML/CSS, JavaScript, jQuery, Webpack, Python, RDKit, PubChem}}{Sep 2025 -- May 2026}
        \resumeItemListStart
          \resumeItem{Enhanced a cheminformatics web application to model chemical odors as graphs and visualize molecular data.}
          \resumeItem{Calculated and mapped chemical functional groups to specific scent profiles using Python, RDKit, and PubChem.}
          \resumeItem{Integrated an automated code obfuscation pipeline into Webpack to effectively secure intellectual property.}
        \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://github.com/roudy-h/dicewars}{Dice Wars}} $|$ \emph{C++}}{Nov 2025 -- Jan 2026}
        \resumeItemListStart
          \resumeItem{Engineered a turn-based strategy game featuring heuristic-driven AI opponents and a procedural map generation system.}
        \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{PolyRisk} $|$ \emph{Python}}{Oct 2025 -- Nov 2025}
        \resumeItemListStart
          \resumeItem{Developed intelligent AI agents for the Risk board game utilizing custom heuristics and Monte Carlo Tree Search (MCTS).}
        \resumeItemListEnd
    
    \resumeProjectHeading
      {\textbf{\href{https://github.com/roudy-h/football-app}{Football App}} $|$ \emph{HTML/CSS, JavaScript, Node.js, Express.js, Passport.js, React, Tailwind CSS}}{Mar 2024 -- Apr 2024}
        \resumeItemListStart
          \resumeItem{Built a full-stack platform fetching and caching external REST API football match results and live statistics.}
          \resumeItem{Engineered a secure multi-user betting competition game utilizing Passport.js for session authentication.}
        \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://github.com/Fisail/Botanicia}{Botanicia}} $|$ \emph{HTML/CSS, JavaScript, PHP, Symfony, MariaDB, Apache}}{Nov 2023 -- Jan 2024}
        \resumeItemListStart
          \resumeItem{Developed a full-stack e-commerce web application for gardening products with CRUD features and user authentication.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Kotlin, Python, C/C++, SQL (Oracle, MariaDB), MongoDB, JavaScript, HTML/CSS, R} \\
     \textbf{Frameworks}{: Spring Boot, Angular, React, Node.js, Flask, JUnit, WordPress, FastAPI} \\
     \textbf{Developer Tools}{: Git, Docker, Kubernetes, Microsoft Azure, VS Code, Visual Studio, IntelliJ,} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
